### 2013-07-05 Tex/chapters/model.tex
normierte T_c

    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:collapse_s_0}
                 \subref{sfig:binder_fit_s_0} Binder cumulant interpolated
                    with cubic splines (the errorbars are too small to see)}
        \label{fig:binder_fit_s_0}
    \end{figure}
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
    for the measured points.
    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
    are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
    is in very good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\

>>>>

    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
                    with cubic splines (the errorbars are too small to see)
                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
                }
        \label{fig:binder_fit_s_0}
    \end{figure}
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
    for the measured points.
    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27 k_{B}\). For
    the sake of simplicity let the Boltzmann constant \(k_{B}=1\) in the
    following.
    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
    are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\),
    which is in good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
    Because \(T_{c}\) is dependend on \(J\) and hence also on the count
    of bounds, the values of \(T_{c}\) will be normalized by the mean
    sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
